Attack Graph Generation for Micro-service Architecture

### 2018-09-14 paper_own_docker/chapters/abstract.tex
TODOs

Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable. This advantage has resulted in a rapid increase in usage of microservices in recent years. Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect. Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.

>>>>

Microservices are increasingly dominating the field of service systems, among their many characterstics, practices are technology heterogeneity and reuse and network interfaces. Therefore, with the increase of utilizing third-party components, the potential vulanrabilities existing in a microservice-based system increase. Based on components dependency, these vulnerabilities lead to exposing critical assets of such systems. Similar problems have been tackled in computer networks communities. In this paper, we propose the utilization of attack graphs as a part of the automated development infrastructure used in microservices-based systems. To that end, we relate microservices to network nodes, and automatically generate attack graphs that help practitioners to identify, analyze, and prevent plausible attack paths on their microservice-based container networks. We present a complete solution that can be easily embeded into the continuous delivery systems, and show with real-world use cases its efficiency and scalability. 
%Breath-first Search (BFS) based method for attack graph generation and security analysis of microservice architectures using Docker

### 2018-09-14 paper_own_docker/chapters/background_microservices.tex
TODOs

As real-world software increases in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability. A software application whose modules cannot be executed independently is called a monolith. Monoliths are characterized by tight coupling, vertical scaling and strong dependence. Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}. However, in a typical SOA, the services are monolithic which gives rise to microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
In the microservices paradigm, multiple services are split into very basic units which are task oriented. According to Dragoni et al. a microservice is a cohesive, independent process interacting via messages. These microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}. Microservice architectures provide us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability among other benefits \cite{newman2015building}. However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.

>>>>

\textbf{TODO} add a brief histroy of ms\\
\textbf{TODO} at the end introduce container based 
As real-world software increases in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability. A software application whose modules cannot be executed independently is called a monolith. Monoliths are characterized by tight coupling, vertical scaling and strong dependence. Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}. However, in a typical SOA, the services are monolithic which gives rise to microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
In the microservices paradigm, multiple services are split into very basic units which are task oriented. According to Dragoni et al. a microservice is a cohesive, independent process interacting via messages. These microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}. Microservice architectures provide us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability among other benefits \cite{newman2015building}. However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.

### 2018-09-14 paper_own_docker/chapters/introduction.tex
TODOs

>>>>

%intro about the new paradiagm of mirocservices its benefits and new oppurnties, maybe its utilization in secuirty/ safety critical systems
Microservices, as a new approach to manage the complexity of modern applications, are increasingly adopted in real-world systems. The new architectural style 
follows the Unix fundamental principles  of decomposing systems into small programs \cite{Unix ideas [115]:} that each fulfills only one cohesive task and can work together using universal interfaces. Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{[Microservices. Martin Fowler(2015)]}. The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{}. However, clearly, other qualities like the network utilization, and the security are negatively affected \cite{ahmadvand2016requirements}.  Balancing the trades-off among these factors derive the decision of using microservices in industry. That said, a non exhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture. This shift is  motivated mainly by the demanding requirements of scalability, time to market, and better optimization of development efforts. We see microservice-based systems in domains of video streaming, social networks, logistics, internet of things \cite{internet}, and smart cities \cite{smartcity}.

% the new tools or eco system of this style, especially container based deployment... the benefits of it and the challanges brought by it, like open source utilization and scurity overhead brought by networks and docker security issues. 
Microservices have popularized two main concepts in the software engineering community. The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in lightweight containers. As a result the systems are deployed as networks of communicating micorservices. Each microservice achieves an independent task. 
% threat modeling as a way to systmatically analyze threats... its benefits and obstecales, ag as an example especially for newtorked systems... the mapping between container based and network applications... and the progress there.

% the problem: summing it up and the solution
% the potentisl benefit in the scope of devops practices and automation (automation should be mentioned before)
% contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
% structure

### 2018-09-14 paper_own_docker/chapters/method.tex
TODOs

\begin{figure}
	\includegraphics[]{./images/Topology_graph}
	\caption{Example topology graph. The topology graph is a subset of a real topology graph from the Netflix OSS example. Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
	\label{TopologyGraph}
\end{figure}

As mentioned above, nodes and edges are the basic building blocks of an attack graph. Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors. In order for an attacker to exploit a given vulnerability, certain preconditions have to be met. Once an attacker exploits this vulnerability, he gains the privilege of the target container as a postcondition and an edge is added to the attack graph. Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}. The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.

Privileges play a central role in this attack graph generation. We model the privileges in a hierarchy. The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine. On the other side, The keyword OS means that the host machine has been compromised. Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}. None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.

@@

In order to show how the attack graph generation works in practice, we present a small example. The example is taken from the Netflix OSS Github repository \cite{netflixoss}. Displayed in Figure \ref{TopologyGraph} is the topology of the example. The topology consists of "Outside" node, "Docker daemon" node and a subset of other nodes. In Figure \ref{AttackGraph} we can see a part of the resulting attack graph. Parts of both graphs have been intentionally omitted to reduce complexity. An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability and gain USER privilege. Then with this USER privilege, it can exploit the CVE-2015-7554 vulnerability on the same container to gain ADMIN privilege. Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 and gain ADMIN privilege. It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka. Another path would be to exploit the CVE-20108-1124 vulnerability while have only USER privilege on Zuul to gain directly ADMIN privileges and then attack the Eureka container. Our attack graph generator shows both paths since it is of an interest to see every possible route in which a container can be compromised.

>>>>

\textbf{TODO} add this image to fig 2 in the same figure and have them as subfigures\\
\begin{figure}
	\includegraphics[]{./images/Topology_graph}
	\caption{Example topology graph. The topology graph is a subset of a real topology graph from the Netflix OSS example. Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
	\label{TopologyGraph}
\end{figure}

As mentioned above, nodes and edges are the basic building blocks of an attack graph. Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels\textbf{TODO}  explain this, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors. In order for an attacker to exploit a given vulnerability, certain preconditions have to be met. Once an attacker exploits this vulnerability, he gains the privilege of the target container as a postcondition and an edge is added to the attack graph. Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}. The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.

\textbf{TODO} explain here why VOS we dont have virtual machines say that we are adapting those to the images\\
Privileges play a central role in this attack graph generation. We model the privileges in a hierarchy. The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine. On the other side, The keyword OS means that the host machine has been compromised. Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}. None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.

@@

\subsubsection{Example}
\textbf{TODO}  explain the example usage what is the system and what is ZUUL and give an example of one of the CVE briefly.\\
In order to show how the attack graph generation works in practice, we present a small example. The example is taken from the Netflix OSS Github repository \cite{netflixoss}. Displayed in Figure \ref{TopologyGraph} is the topology of the example. The topology consists of "Outside" node, "Docker daemon" node and a subset of other nodes. In Figure \ref{AttackGraph} we can see a part of the resulting attack graph. Parts of both graphs have been intentionally omitted to reduce complexity. An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability and gain USER privilege. Then with this USER privilege, it can exploit the CVE-2015-7554 vulnerability on the same container to gain ADMIN privilege. Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 and gain ADMIN privilege. It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka. Another path would be to exploit the CVE-20108-1124 vulnerability while have only USER privilege on Zuul to gain directly ADMIN privileges and then attack the Eureka container. Our attack graph generator shows both paths since it is of an interest to see every possible route in which a container can be compromised.
